---
title: "logistic regression homework"
author: "Teerapat H."
date: "2024-08-08"
output: html_document
---

# Build model to survive prediction.

Using data from "Titanic" library.

### Start from install by using install.package() function, and import library.

```{r}
install.packages("titanic")
library(titanic)
```

### And then cleansing data using na.omit() function.

```{r}
titanic_train = na.omit(titanic_train)
```

Then, time to following by building model golden rules.

### Split.

```{r}
n = nrow(titanic_train)
set.seed(42)
id = sample(1:n, n*0.75)
train_data = titanic_train[id, ]
test_data = titanic_train[-id, ]
```

I will split 75% of data from "titanic_train" to train model, and use another 25% left to test model.

### Train

```{r}
model = glm(Survived ~ Pclass + Sex + Age, 
            data = train_data, family = "binomial")
```

### Test

```{r}
df = data.frame(test_data$Pclass,
                test_data$Sex,
                test_data$Age,
                test_data$Survived)

df$prob_surv = predict(model, newdata = test_data, type = "response")
df$pred_surv = ifelse(df$prob_surv >= 0.5, 1, 0)
```

### Model evaluation.

Now, time to evaluate model.

Start from create confusion matrix using table() function, and stored in "confusion_matrix" variable for reusable.

```{r}
confusion_matrix = table(df$pred_surv, 
               df$test_data.Survived, 
               dnn = c("predicted", "Actual"))
```

Then calculate another value accuracy, precision, recall and F1 score included.

```{r}
acc = (confusion_matrix[1,1] + confusion_matrix[2,2]) / sum(confusion_matrix)
cat("Accuracy:", acc)

prec = confusion_matrix[2,2] / (confusion_matrix[2,1] + confusion_matrix[2,2])
cat("Precision:", prec)

rec = confusion_matrix[2,2] / (confusion_matrix[1,2] + confusion_matrix[2,2])
cat("Recall:", rec)

f1 = 2 * (prec * rec) / (prec + rec)
cat("F1 score:", f1)
```

Calculated by using normal operation. access value by subset method.
